---
title: "Weight of Fish"
author: "Alexis Velasco"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(leaps)

```
```{r}
All_Fish<- read.csv(file="Fish.csv")
```
```{r}
Perch<- filter(All_Fish,Species=="Perch")
```
```{r}
Perch<- select(Perch, -Species)
```
 



# Predicting Fish Weight


## Perch

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```


### Best Models
The best model to use for Perch would be height and width.It is considered the best model because it has the highest adjusted R^2 allowing it to sit at the top of the graph,with a y of 0.9400 making it bigger and higher up than the rest of the subsets. 

### Best Two regressor model
The best two regressor model would also be height and width, because adjusted R^2 test out all the levels, giving the these two as the best with the subset size of 2. 
 

## Pike

```{r}
Pike<- filter(All_Fish,Species=="Pike")
```
```{r}
Pike<- select(Pike, -Species)
```


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Models
The best models are length1 ,length2, length3, height and width. It is considered the best model because it  had the highest adjusted R^2 allowing it to sit at the top of the graph, with a y height sqre of 0.980, making it bigger and higher up than the rest. 

### Best Two regressor model
The best two regressor model is length1 and length2, because adjusted R^2 test out all the levels, giving the these two as the best subsets. 

## Roach

```{r}
Roach<- filter(All_Fish,Species=="Roach")
```
```{r}
Roach<- select(Roach, -Species)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Models
The best models are length3 and width. It is considered the best model because it  had the highest adjusted R^2 allowing it to sit at the top of the graph, with a y height sqre of 0.850, making it bigger and higher up than the rest. 

### Best Two regressor model
The best two regressor model is length3 and width, because adjusted R^2 test out all the levels, giving the these two as the best subsets with a subset size of two, but it is the same as the best model overall. 

## Final Summary Statements
For each fish we used an adjusted R^2 model that showed which variables were best to determine the best way to predict the weight each fish. For perch and roach only two variables were required to get the best prediction. Having the common variable of width but Perch using height and roach using length3 as their second variables. However Pike needed all factors taken into account to predict the best weight. For perch and roach the best models were the same as the best two best regressor models. Although the Pike's two best regressor model is variable length1 and length2.

