---
title: "Weight of Fish"
author: "Alexis Velasco"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(leaps)
```
```{r}
All_Fish<- read.csv(file="Fish.csv")
```
```{r}
Perch<- filter(All_Fish,Species=="Perch")
```
```{r}
Perch<- select(Perch, -Species)
```
 



# Predicting Fish Weight


## Perch

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```


### Best Models
The best model to use for Perch would be height and width.It is considered the best model because it has the highest adjusted R^2 allowing it to sit at the top of the graph,with a y of 0.9400 making it bigger and higher up than the rest of the subsets. 

### Best Two regressor model
The best two regressor model would be height and width, because adjusted R^2 test out all the levels, giving the these two as the best subsets. 
 

## Pike

```{r}
Pike<- filter(All_Fish,Species=="Pike")
```
```{r}
Pike<- select(Pike, -Species)
```


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Models
The best models are length1 ,length2, length3, height and width. It is considered the best model because it  had the highest adjusted R^2 allowing it to sit at the top of the graph, with a y height sqre of 0.980, making it bigger and higher up than the rest. 

### Best Two regressor model
The best two regressor model is length1 and length2, because adjusted R^2 test out all the levels, giving the these two as the best subsets. 

## Roach
```{r}
Roach<- filter(All_Fish,Species=="Roach")
```
```{r}
Roach<- select(Roach, -Species)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
### Best Models

The best models are length3 and width. It is considered the best model because it  had the highest adjusted R^2 allowing it to sit at the top of the graph, with a y height sqre of 0.850, making it bigger and higher up than the rest. 

### Best Two regressor model
The best two regressor model is length3 and width, because adjusted R^2 test out all the levels, giving the these two as the best subsets with a subset size of two, but it is the same as the best model overall. 

## Final Summary Statements